TITLE

### 2021-02-19 outputs/paper/paper.Rmd

---
title: "TITLE"
author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  bookdown::pdf_document2:
    toc: no
subtitle: "SUBTITLE"
abstract: "ABSTRACT"
thanks: 'Code and data are available at: [github.com/amycfarrow/ontariorestaurantclosuresexperiment](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment).'
bibliography: references.bib
---

@@

@@

@@

The stratification was used because there were very differently sized LHAs, and randomly selecting only 12 LHAs from a list of 33 left too high a likelihood of nonequivalent treatment and control groups.

@@

@@

@@

@@

@@

```{r survey1summary, echo = FALSE, message = FALSE, warning = FALSE}
survey_1 %>% 
  summary_factorlist("group", c("service_type", "disability", "woman", "indigenous", "visible", "revenue", "ft", "pt"),
                     p = FALSE, 
                     add_dependent_label = TRUE, 
                     dependent_label_prefix = "",
                     add_col_totals = TRUE,
                     include_row_missing_col = FALSE,
                     col_totals_rowname = "",
                     col_totals_prefix = "N = ",
                     total_col = FALSE) %>%
  mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
  knitr::kable(caption = "Summary statistics for treatment and control baselines",
               booktabs = TRUE,
               col.names = c("", "", "Treatment", "Control")) %>%
  kableExtra::kable_styling()
```

```{r baselinerevenue, fig.cap="Revenue distribution for treatment and control baselines, from Survey 1", fig.width=10, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
ggplot(survey_1, aes(x = revenue / 1000, fill = group)) +                       
  geom_histogram(position = "dodge", binwidth = 5) +
  theme_minimal() +
  scale_x_continuous(breaks = c(0, 50, 100, 150, 200, 250, 300)) +
  labs(fill = NULL,
       x = "Revenue in May 2021 (in thousands of Canadian dollars)",
       y = "Number of restaurants")
```

@@

@@

```{r survey2summary, echo = FALSE, message = FALSE, warning = FALSE}
survey_2 %>% 
  summary_factorlist("group", c("service_type", "disability", "woman", "indigenous", "visible", "shutdown", "revenue", "ft", "pt"),
                     p = FALSE, 
                     add_dependent_label = TRUE, 
                     dependent_label_prefix = "",
                     add_col_totals = TRUE,
                     include_row_missing_col = FALSE,
                     col_totals_rowname = "",
                     col_totals_prefix = "N = ",
                     total_col = FALSE) %>%
  mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Closure", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
  knitr::kable(caption = "Summary statistics for treatment and control groups post-treatment",
               booktabs = TRUE,
               col.names = c("", "", "Treatment", "Control")) %>%
   kableExtra::kable_styling()
```

@@

@@

```{r servicetypeimpact, fig.cap="Revenues more heavily impacted for dine-in only establishments", fig.width=6, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
survey_2 %>%
  filter(service_type != "NA") %>%
  ggplot(aes(x = service_type, y = revenue / 1000, fill = group)) +
  geom_bar(position = "dodge", stat = "summary", fun.y = mean) +
  labs(fill = NULL,
       x = "Service type provided",
       y = "Mean revenue (in thousands of Canadian dollars") +
  scale_x_discrete(labels = c( "Dine-in Only", "Take-out only", "Both")) +
  theme_minimal()
```

@@

```{r minorityimpact, fig.cap="Minority-owned businesses were more heavily impacted", fig.width=6, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
bind_rows(
  survey_2 %>%
    filter(indigenous == "yes" | visible == "yes") %>%
     mutate(minority = "Visible minority / Indigenous")
  ,
  survey_2 %>%
   filter(indigenous == "no" & visible == "no") %>%
    mutate(minority = "No")
) %>% 
  mutate(minority = fct_relevel(minority, "Visible minority / Indigenous", "No")) %>%
  ggplot(aes(x = minority, y = revenue / 1000, fill = group)) +
  geom_bar(position = "dodge", stat = "summary", fun.y = mean) +
  labs(fill = NULL,
       x = "Racial and ethic minorities",
       y = "Mean revenue (in thousands of Canadian dollars") +
  theme_minimal()
```

@@

@@

Survey non-response.

>>>>

---
title: "TITLE"
author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  bookdown::pdf_document2:
    toc: no
subtitle: "SUBTITLE"
abstract: "Four sentences. 1) what was done, 2) what was found, and 3) why this matters (all at a high level). Top level finding"
thanks: 'Code and data are available at: [github.com/amycfarrow/ontariorestaurantclosuresexperiment](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment).'
bibliography: references.bib
---

@@

<<<<tells a reader everything they need to know, including putting it into a broader context.>>>>

The experiment was comissioned by ___.

<<<<<<you’re interested in, what you did, what you found, why it’s important, etc.>>>>>>>>

<<<Outline paper structure>>>

@@

## Methodology

@@

The stratification was used because there were very differently sized LHAs, and randomly selecting only 12 LHAs from a list of 33 left too high a likelihood of nonequivalent treatment and control groups. Given the limitations of cluster sampling, stratifying the clusters by size helped ensure the experiment would be representative of Ontario. <stuff about the statistical properties of cluster and stratified sampling somewhere in here, cite textbook reading>.

@@

The demographic information was collected so that disparate impacts on different communities could be identified.
Revenue and number of employees were collected as measures of the restaurant's performance and impact on the local employment levels. These were the primary indicators of interest, due to the <GOVERNMENT ORGANIZATION>>>>> focus on economic stability and employment levels.

@@

<Something about enforcement of closures-- how have fines worked during covid closures?)

Because it is very difficult for a restaurant to move location in under two weeks, the control and treatment groups were effectively separated.

@@

<<<<<<<<<<<<survey strengths and weaknesses>>>>>>>>>>>>>

@@

<<<<<Consider: do we need to plot more raw data?>>>>>>>>>>>

It was necessary to collect data before the intervention to establish that the treatment and control groups were in fact comparable.

@@

```{r survey1summary, echo = FALSE, message = FALSE, warning = FALSE}
survey_1 %>% 
  summary_factorlist("group", c("service_type", "disability", "woman", "indigenous", "visible", "revenue", "ft", "pt"),
                     p = FALSE, 
                     add_dependent_label = TRUE, 
                     dependent_label_prefix = "",
                     add_col_totals = TRUE,
                     include_row_missing_col = FALSE,
                     col_totals_rowname = "",
                     col_totals_prefix = "N = ",
                     total_col = FALSE) %>%
  mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
  knitr::kable(caption = "Summary statistics for treatment and control baselines",
               booktabs = TRUE,
               col.names = c("", "", "Treatment", "Control")) %>%
  kableExtra::kable_styling(latex_options = "striped", stripe_index =c(1,5:7,11:13,17:19))
```

```{r baselinerevenue, fig.cap="Revenue distribution for treatment and control baselines, from Survey 1", fig.width=10, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
ggplot(survey_1, aes(x = revenue / 1000, fill = group)) +                       
  geom_histogram(position = "dodge", binwidth = 5) +
  theme_minimal() +
  scale_x_continuous(limits = c(0, 250), breaks = c(0, 50, 100, 150, 200, 250, 300)) +
  labs(fill = NULL,
       x = "Revenue in May 2021 (in thousands of Canadian dollars)",
       y = "Number of restaurants")
```

@@

<<<<<Consider: do we need to plot more raw data?>>>>>>>>>>>

@@

```{r survey2summary, echo = FALSE, message = FALSE, warning = FALSE}
survey_2 %>% 
  summary_factorlist("group", c("service_type", "disability", "woman", "indigenous", "visible", "shutdown", "revenue", "ft", "pt"),
                     p = FALSE, 
                     add_dependent_label = TRUE, 
                     dependent_label_prefix = "",
                     add_col_totals = TRUE,
                     include_row_missing_col = FALSE,
                     col_totals_rowname = "",
                     col_totals_prefix = "N = ",
                     total_col = FALSE) %>%
  mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Closure", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
  knitr::kable(caption = "Summary statistics for treatment and control groups post-treatment",
               booktabs = TRUE,
               col.names = c("", "", "Treatment", "Control")) %>%
   kableExtra::kable_styling(latex_options = "striped", stripe_index =c(1,5:7,11:13,17:19))
```

@@

<<< overview of the results>>>

<<<how they fit in existing literature -- need some references here>>>>

@@

```{r servicetypeimpact, fig.cap="Revenues more heavily impacted for dine-in only establishments", fig.width=6, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
survey_2 %>%
  filter(service_type != "NA") %>%
  ggplot(aes(x = service_type, y = revenue / 1000, fill = group)) +
  geom_bar(position = "dodge", stat = "summary", fun.y = mean) +
  labs(fill = NULL,
       x = "Service type provided",
       y = "Mean revenue (in thousands of Canadian dollars") +
  scale_x_discrete(labels = c( "Dine-in Only", "Take-out only", "Both")) +
  theme_minimal()
```

@@

```{r minorityimpact, fig.cap="Minority-owned businesses were more heavily impacted", fig.width=5, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
bind_rows(
  survey_2 %>%
    filter(indigenous == "yes" | visible == "yes") %>%
     mutate(minority = "Visible minority / Indigenous")
  ,
  survey_2 %>%
   filter(indigenous == "no" & visible == "no") %>%
    mutate(minority = "No")
) %>% 
  mutate(minority = fct_relevel(minority, "Visible minority / Indigenous", "No")) %>%
  ggplot(aes(x = minority, y = revenue / 1000, fill = group)) +
  geom_bar(position = "dodge", stat = "summary", fun.y = mean) +
  labs(fill = NULL,
       x = "Racial and ethnic minorities",
       y = "Mean revenue (in thousands of Canadian dollars") +
  theme_minimal()
```

@@

## Ethics ? Or integrate in other sections.

@@

Survey non-response. Figure \@ref(fig:nonresponse)

```{r nonresponse, fig.cap="More than half of surveyed restaurants did not respond", fig.width=8, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
num_treat_sample <- as.numeric(count(table_for_surveys %>% filter(group == "treatment")))

num_control_sample <- as.numeric(count(table_for_surveys %>% filter(group == "control")))

num_treat_complete_survey1 <- sum(complete.cases(survey_1 %>% filter(group == "treatment")))

num_control_complete_survey1 <- sum(complete.cases(survey_1 %>% filter(group == "control")))

num_treat_partial_survey1 <- sum(!complete.cases(survey_1 %>% filter(group == "treatment")))

num_control_partial_survey1 <- sum(!complete.cases(survey_1 %>% filter(group == "control")))

num_treat_nonre_survey1 <- num_treat_sample - num_treat_complete_survey1 - num_treat_partial_survey1

num_control_nonresurvey1 <- num_control_sample - num_control_complete_survey1 - num_control_partial_survey1

num_treat_complete_survey2 <- sum(complete.cases(survey_2 %>% filter(group == "treatment")))

num_control_complete_survey2 <- sum(complete.cases(survey_2 %>% filter(group == "control")))

num_treat_partial_survey2 <- sum(!complete.cases(survey_2 %>% filter(group == "treatment")))

num_control_partial_survey2 <- sum(!complete.cases(survey_2 %>% filter(group == "control")))

num_treat_nonre_survey2 <- num_treat_sample - num_treat_complete_survey2 - num_treat_partial_survey2

num_control_nonresurvey2 <- num_control_sample - num_control_complete_survey2 - num_control_partial_survey2

tibble(Group = c("Treatment", "Control", "Treatment", "Control", "Treatment", "Control", "Treatment", "Control", "Treatment", "Control", "Treatment", "Control"), 
        Response = c("Complete", "Complete", "Partial", "Partial", "No response", "No response", "Complete", "Complete", "Partial", "Partial", "No response", "No response"), 
        Survey = c("Survey 1", "Survey 1","Survey 1","Survey 1","Survey 1","Survey 1", "Survey 2", "Survey 2", "Survey 2", "Survey 2", "Survey 2", "Survey 2"), 
        Count = c(num_treat_complete_survey1, num_control_complete_survey1, num_treat_partial_survey1, num_control_partial_survey1, num_treat_nonre_survey1, num_control_nonresurvey1,
          num_treat_complete_survey2, num_control_complete_survey2, num_treat_partial_survey2, num_control_partial_survey2, num_treat_nonre_survey2, num_control_nonresurvey2)) %>%
  ggplot(aes(x = Response, y = Count, fill = Group)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~Survey) +
  theme_minimal()
